---
title: "eds-212-day5-comp1"
format: 
  html:
    code-fold: true
    code-summary: "show me the code"
editor: visual
execute:
  echo: false
  warning: false
---

```{r}
library(tidyverse)
```

## Explore starwars dataset

-   look at the first 6 lines of starwars

-   find the dimensions of starwars

-   make a histogram of character heights

-   make a scatterplot of height vs weight

```{r}

dim(starwars)

head(starwars)
```

```{r}
ggplot(data = starwars, aes(x = height)) + geom_histogram(fill = "black", color = "yellow") + theme_minimal()
```

```{r}
ggplot(data = starwars, aes(x = height, y = mass)) + geom_point(color = "black") + theme_minimal()
```

## Calculate summary statistics

Use mean() function to find means.

Use sd() function to find standard deviations.

```{r}
mean_height <- mean(starwars$height, na.rm = TRUE)

mean_height
```

Find and stare the standard deviation of character heights:

```{r}
sd_height <- sd(starwars$height, na.rm = TRUE)
sd_height
```

## In-line reporting using code outputs

The mean height of star wars characters is 174.38 cm with a standard deviation of 34.8 cm. \<- wrong

The mean height of star wars characters is `r mean_height` cm with a standard deviation of `r sd_height` cm
